Displacement of fishing effort by Large Scale Marine Protected Areas

### 2018-09-29 docs/Manuscript.tex
Updated latest analyses and manuscript

\documentclass[]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={Displacement of fishing effort by Large Scale Marine Protected Areas},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{natbib}
\bibliographystyle{nature}
\usepackage{longtable,booktabs}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

  \title{Displacement of fishing effort by Large Scale Marine Protected Areas}
    \pretitle{\vspace{\droptitle}\centering\huge}
  \posttitle{\par}
  \subtitle{Updated on 2018-09-27}
  \author{Juan Carlos Villaseñor-Derbez\textsuperscript{1} John
Lynham\textsuperscript{2}}
    \preauthor{\centering\large\emph}
  \postauthor{\par}
      \predate{\centering\large\emph}
  \postdate{\par}
    \date{\textsuperscript{1}Bren School of Environmental Science and Management,
University of California Santa Barbara, Santa Barbara, CA
\textsuperscript{2}Department of Economics, University of Hawaii at
Manoa, Honolulu, HI}

\usepackage{float}
\floatplacement{figure,table}{H}
\usepackage{lineno}
\linenumbers

@@

{
\setcounter{tocdepth}{4}
\tableofcontents
}
\clearpage

@@

This section is divided into two main parts. First, we provide a general
description of AIS data and the process of identification of
vessel-level events done by Global Fishing Watch \footnote{\href{globalfishingwatch.org}{Global
  Fishing Watch}}. Alongside, we describe the subset of data that we use
for these analyses. When relevant, we also point out possible
shortcommings in the data, or factors that must be considered in the
later analyses. Then we move on to explain our identification strategy,
and the main analyses that we undertake.

@@

Automatic Identification Systems are on-board devices intended to
provide at-sea saftey and prevent ship collisions by broadcasting vessel
locations to surrounding vessels. These broadcasted positions can be
recorded by satellites and land-based antenas. GFW uses a neural network
to infer vessel characteristics and whether each broadcasted position
represents a fishing event, thus allowing us to estimate near real-time
fishing events globally \citep{kroodsma_2018}. The recent addition of
satellites that can receive AIS signals causes an apparent increase in
the number of broadcasted AIS messages (\emph{i.e.} points) and
therefore fishing hours. It is therefore important to be cautious when
comparing temporal trends. The variability in AIS data and dynamic ocean
conditions require that temporal trends be taken into account. We do
that by incorporating a series of controls, which are defined in the
following section.

@@

The GFW data contain 233 purse seiners and longliners that have fished
within PIPA waters. From these, only 217 did so at least once before
2015, but only 183 continued to fish after 2015\footnote{The 34 missing
  vessels might have exited the fishery, been decomissioned or sold
  (therefore chaning their AIS and mmsi), or turned off their AIS
  transmiters. On either case, we are not able to observe these.}.
Vessels that fished within PIPA before implementation might stop fishing
afterwards, therefore not being observable in the post-treatment period.
New vessels might have also entered the fishery after PIPA closure, and
were likely not exposed to the policy intervention in the pre-treatment
period. Therefore, we define our treatment and control groups as
follows. The treatment group contains all vessels that fished within
PIPA at least once before the closure, and that continued to fish
elsewhere afterwards. The control group has vessels that never fished
within PIPA waters, belong to other PNA countries, and have fished in
surrounding areas (\emph{i.e.} PNA-countries' EEZ) before and after PIPA
closure. Figure \ref{fig:baci_strict} provides a visual representation
of the vessel-level that make up each of group through time.

Tables \ref{tab:baci_n}, \ref{tab:baci_n_s}, and \ref{tab:baci_h} show
the number of vessels, number of vessels following a BACI design, and
fishing hours, respectively. Tables show data grouped by gear
(longlines, purse seines), group (treated, control), and period (before,
after). The relative change (After / Before) is also shown. Table
\ref{tab:baci_n} shows information for all fishing vessels in the
dataset, while Tables \ref{tab:baci_n_s} and \ref{tab:baci_h} show
information for vessels that meet the BACI design (i.e.~excludes vessels
that only appear at one point in time).

\begin{figure}
\centering
\includegraphics{../img/BACI_strict_gear.png}
\caption{\label{fig:baci_strict}Stream of fishing events by vessels
(stacked on the y-axis due to space) through time (x-axis). Each dot
represent a vessel-month, with colors indicating the pre and post
periods, and pannels separating between gear and treated or control
groups.}
\end{figure}

@@

\caption{\label{tab:unnamed-chunk-4}\label{tab:baci_n}Number of fishing vessels (identified by mmsi) for each gear before and after PIPA implementation.}
\centering
\begin{tabular}[t]{llrrr}
\toprule
Gear & Treatment & Before & After & Change (A / B)\\
\midrule
drifting\_longlines & FALSE & 105 & 218 & 2.0761905\\
drifting\_longlines & TRUE & 139 & 118 & 0.8489209\\
purse\_seines & FALSE & 49 & 89 & 1.8163265\\
purse\_seines & TRUE & 78 & 81 & 1.0384615\\
\bottomrule
\end{tabular}
\end{table}

@@

\caption{\label{tab:unnamed-chunk-5}\label{tab:baci_n_s}Number of fishing vessels (identified by mmsi) for each gear before and after PIPA implementation.}
\centering
\begin{tabular}[t]{llrrr}
\toprule
Gear & Treatment & Before & After & Change (A / B)\\
\midrule
drifting\_longlines & FALSE & 88 & 88 & 1\\
drifting\_longlines & TRUE & 115 & 115 & 1\\
purse\_seines & FALSE & 38 & 38 & 1\\
purse\_seines & TRUE & 68 & 68 & 1\\
\bottomrule
\end{tabular}
\end{table}

\caption{\label{tab:unnamed-chunk-6}\label{tab:baci_h}Mean fishing hours for each gear before and after}
\centering
\begin{tabular}[t]{llrrr}
\toprule
Gear & Treatment & Before & After & Change (A / B)\\
\midrule
drifting\_longlines & FALSE & 481.42502 & 473.5823 & 0.9837094\\
drifting\_longlines & TRUE & 548.22580 & 524.8121 & 0.9572919\\
purse\_seines & FALSE & 66.50483 & 172.3775 & 2.5919548\\
purse\_seines & TRUE & 56.87322 & 146.2015 & 2.5706563\\
\bottomrule
\end{tabular}
\end{table}

@@

\subsubsection{Change in behavior}\label{change-in-behavior}

@@

\[
y_{i,t} = \alpha + \beta_1 Post_t + \beta_2 Treat_i + \beta_3 Post_t \times Treat_i + \mu_t + \phi_t + \gamma_i + \epsilon_{i,t}
\]

Where \(y_{ijkl}\) is the variable of interest for vessel \(i\) in time
period \(t\). A dummy variable \(Post_i\) takes the value of 0 for all
dates prior to PIPA implementation and a value of 1 por all dates
including and following PIPA implementation. \(Treat_i\) is a dummy
variable indicating whether a vessel belongs to the control
(\(Treat_i = 0\)) or treatment (\(Treat_i = 1\)) group. \(\alpha\) is
the standard intercept, \(\beta_1\) captures the \emph{ex post} change,
\(\beta_2\) captures the difference between treated and control groups,
and \(\beta_3\) is our parameter of interest: de DiD estimate capturing
the treatment effect. Finally, \(\mu_t\), \(\phi_t\), and \(\gamma_i\)
represent month-, year-, and flag-level dummies that account for
seasonality or country-level management interventions.

\subsubsection{Vessel displacement and
redistribution}\label{vessel-displacement-and-redistribution}

Our second part of the analyses focuses on the redistribution of fishing
effort. In other words, identifying where do vessels that used to fish
inside PIPA go after its establishment. We calculate the monthly
relative distribution of fishing hours by all treated vessels across all
fished EEZs and the high seas. These trends are shown in Figure
\ref{fig:redist_trend}. EEZs that had sproadic fishing events were
pooled into a group of ``others'', leaving us with a total of n = 12
spatially defined regions (\emph{i.e.} EEZs, High Seas, ``other EEZs'').
Figure \ref{fig:redist_trend_spa} shows the yearly average of the
relative spatial allocation of fishing efforts; this is the spatial
representation of \ref{fig:redist_trend} averaged by year.

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-9-1.pdf}
\caption{\label{fig:unnamed-chunk-9}\label{fig:redist_trend}}
\end{figure}

@@

@@

Fig. \ref{fig:all_vessels} shows that mean fishing hours for purse
seiners have an abrupt increase, just before January 1st, 2015. This
trend is observed for both treated and control groups. Longliners,
however, show a more stable trend. The number of mmsi codes increases
through time. This can largel be explained by the addition of more
satellits, which increasedetectability of vessels. As expected total
fishing hours follow a similar trend to that of mmsi numbers. Results of
the regressions for each gear type are shown in Tables \ref{tab:purse}
and \ref{tab:long}. Column (1) presents the DiD regression with no fixed
effects, column (2) includes month fixed effects, column (3) includes
month and year fixed effects, and column (4) includes month, year, and
flag fixed effects. Figures \ref{fig:puse} and \ref{fig:long} represent
the same coefficient estimates.

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-11-1.pdf}
\caption{\label{fig:unnamed-chunk-11}\label{fig:all_vessels}Fishing hours
and number of vessels by month for all vessels. Vertical dashed line
indicates PIPA closure.}
\end{figure}

>>>>

\documentclass[12pt,]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={Displacement of fishing effort by Large Scale Marine Protected Areas},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{natbib}
\bibliographystyle{plainnat}
\usepackage{longtable,booktabs}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

  \title{Displacement of fishing effort by Large Scale Marine Protected Areas}
    \pretitle{\vspace{\droptitle}\centering\huge}
  \posttitle{\par}
  \subtitle{Updated on 2018-09-28}
  \author{Juan Carlos Villaseñor-Derbez\textsuperscript{1} John
Lynham\textsuperscript{2}}
    \preauthor{\centering\large\emph}
  \postauthor{\par}
      \predate{\centering\large\emph}
  \postdate{\par}
    \date{\textsuperscript{1}Bren School of Environmental Science and Management,
University of California Santa Barbara, Santa Barbara,
CA\newline\textsuperscript{2}Department of Economics, University of
Hawaii at Manoa, Honolulu, HI}

\usepackage{float}
\floatplacement{figure}{H}
\usepackage{lineno}
\linenumbers

@@

@@

This section is divided into two main parts. First, we provide a general
description of AIS data and the process of identification of
vessel-level events done by Global Fishing Watch\footnote{Global Fishing
  Watch: \url{globalfishingwatch.org}}. Alongside, we describe the
subset of data that we use for these analyses. When relevant, we also
point out possible shortcommings in the data, or factors that must be
considered in the later analyses. Then we move on to explain our
identification strategy, and the main analyses that we undertake.

@@

Automatic Identification Systems are on-board devices intended to
provide at-sea saftey and prevent ship collisions by broadcasting vessel
locations to surrounding vessels. These broadcasted positions can be
recorded by satellites and land-based antenas. GFW uses a neural network
to infer vessel characteristics and whether each broadcasted position
represents a fishing event, thus allowing us to estimate near real-time
fishing events globally since 2012 \citep{kroodsma_2018}. The recent
addition of satellites that can receive AIS signals causes an apparent
increase in the number of broadcasted AIS messages (\emph{i.e.} points)
and therefore fishing hours. The variability in AIS data and ocean
conditions require that temporal trends be taken into account. We do
that by incorporating a series of controls, which are defined in the
following section.

@@

Our data contain over 45 million individual AIS messages for 371 purse
seiners and longliners. A total of 233 vessels have fished within PIPA
waters; 217 did so at least once before 2015. However, not all vessels
continued to fish elsewhere after PIPA implementation: 34 vessels have
no recorded AIS messages after 2015\footnote{The 0 missing vessels might
  have exited the fishery, been decomissioned or sold (therefore
  changing their AIS and mmsi), or turned off their AIS transmiters. In
  either case, we are not able to observe these.}, leaving us with 183
vessels that fished inside PIPA before its implementation, and continued
to fish elsewhere afterward. Vessels that fished within PIPA before
implementation might stop fishing afterwards, therefore not being
observable in the post-treatment period. New vessels might have also
entered the fishery after PIPA closure, and were likely not exposed to
the policy intervention in the pre-treatment period. Therefore, we
define our treatment and control groups as follows.

The treatment group contains all vessels (n = 183) that fished within
PIPA at least once before the closure, and that continued to fish
elsewhere afterwards. Vessels in the control group meet al three of the
following conditions: i) Vessels never fished within PIPA waters, ii)
vessels belong to other PNA countries, and iii) vessels have fished in
surrounding areas (\emph{i.e.} PNA-countries' EEZ) before and after PIPA
closure. For each vessel meeting these characteristics, we calculate
their total monthly fishing hours. Figure \ref{fig:baci_strict} provides
a visual representation of the vessel-level streams of fishing events
that make up each group through time. Tables \ref{tab:baci_n_s} and
\ref{tab:baci_h} show the number of vessels following a BACI design, and
fishing hours, respectively. Tables show data grouped by gear
(longlines, purse seines), group (treated, control), and period (before,
after). The relative change in fishing hours (After / Before) is also
shown.

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-4-1.pdf}
\caption{\label{fig:unnamed-chunk-4}\label{fig:baci_strict}Stream of fishing
events by vessels through time. Each line represents a vessel, with dots
indicating months with fishing activity and colors indicating the pre
and post periods. Pannels separating between gear and treated or control
groups.}
\end{figure}

@@

\caption{\label{tab:unnamed-chunk-5}\label{tab:baci_n_s}Number of fishing vessels (identified by mmsi) by gear and treatment group.}
\centering
\begin{tabular}[t]{llr}
\toprule
Gear & Treatment & n\\
\midrule
drifting\_longlines & FALSE & 85\\
drifting\_longlines & TRUE & 115\\
purse\_seines & FALSE & 36\\
purse\_seines & TRUE & 68\\
\bottomrule
\end{tabular}
\end{table}

@@

\caption{\label{tab:unnamed-chunk-6}\label{tab:baci_h}Mean fishing hours and relative change by gear and treatment group.}
\centering
\begin{tabular}[t]{llrrr}
\toprule
Gear & Treatment & Before & After & Change (A / B)\\
\midrule
drifting\_longlines & FALSE & 474.47780 & 462.5491 & 0.9748593\\
drifting\_longlines & TRUE & 544.61935 & 522.8392 & 0.9600085\\
purse\_seines & FALSE & 59.49026 & 154.5776 & 2.5983673\\
purse\_seines & TRUE & 52.91534 & 131.5452 & 2.4859561\\
\bottomrule
\end{tabular}
\end{table}

@@

@@

\[
y_{i,t} = \alpha + \beta_1 Post_t + \beta_2 Treat_i + \beta_3 Post_t \times Treat_i + \mu_1Y_t + \mu_2Y_t^2 + \phi_t + \gamma_i + \epsilon_{i,t}
\]

Where \(y_{i,t}\) is the variable of interest for vessel \(i\) in time
period \(t\). A dummy variable \(Post_i\) takes the value of 0 for all
dates prior to PIPA implementation and a value of 1 por all dates
including and following PIPA implementation. \(Treat_i\) is a dummy
variable indicating whether a vessel belongs to the control
(\(Treat_i = 0\)) or treatment (\(Treat_i = 1\)) group. \(\alpha\) is
the standard intercept, \(\beta_1\) captures the \emph{ex post} change,
\(\beta_2\) captures the difference between treated and control groups,
and \(\beta_3\) is our parameter of interest: de DiD estimate capturing
the treatment effect. Finally, \(\mu_1\) and \(\mu_2\) are coefficients
for a second order polynomial for years (\(Y_t\))\footnote{An earlier
  specification included years as a dummy variable. Such results are
  included in the appendx.}, while \(\phi_t\) and \(\gamma_i\) represent
month-, and flag-level dummies that account for seasonality or
country-level management interventions.

Our second part of the analyses focuses on the redistribution of fishing
effort. In other words, identifying where do vessels that used to fish
inside PIPA go after its establishment. We calculate the monthly
relative distribution of fishing hours by all treated vessels across all
fished EEZs and the high seas. These trends are shown in Figures
\ref{fig:redist_trend_ps} and \ref{fig:redist_trend_ll}, and the
relative change is presented in Table \ref{tab:ba_disp}. EEZs that had
sproadic fishing events were pooled into a group of ``others'', leaving
us with a total of n = 12 and n = 10 spatially defined regions
(\emph{i.e.} EEZs, High Seas, ``other EEZs'') for purse seiners and
longliners, respectively.

@@

All regression coefficients were estimatedd via ordinary least squares,
and heteroskedastic-robust standard errors were calculated. All analyses
were performed in R version 3.5.1) \citep{rcore_2018}. Raw data and code
used in this work are available on
\href{https://github.com/jcvdav/MPA_displacement}{github}.

\caption{\label{tab:unnamed-chunk-9}\label{tab:ba_disp}}
\centering
\begin{tabular}[t]{lrr}
\toprule
country & Longliners & Purse seiners\\
\midrule
PIPA & -11.48 & -8.54\\
KIR & 1.28 & 2.76\\
HS & 0.00 & 0.00\\
COK & 0.00 & 0.34\\
FSM & 0.00 & 0.55\\
\addlinespace
MHL & NA & -0.55\\
NRU & 0.00 & 0.16\\
PNG & 0.00 & -10.02\\
SLB & -8.48 & 2.13\\
TKL & NA & 0.19\\
\addlinespace
TUV & 7.23 & 1.47\\
others & 22.55 & 11.51\\
\bottomrule
\end{tabular}
\end{table}

@@

Our data suggest that purseiners and longliners have different responses
to the implementation of a Large-Scale Marine Protected Area. Fig.
\ref{fig:all_vessels} shows that mean fishing hours for purse seiners
have an abrupt increase, just before January 1st, 2015. This trend is
observed for both treated and control groups. Longliners, however, show
a more stable trend. The number of mmsi codes increases through time.
This can largely be explained by the addition of more satellites, which
increase detectability of vessels. As expected, total fishing hours
follow a similar trend to that of mmsi numbers.

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-10-1.pdf}
\caption{\label{fig:unnamed-chunk-10}\label{fig:all_vessels}Fishing hours
and number of vessels by month for all vessels. Vertical dashed line
indicates PIPA closure.}
\end{figure}

Our DiD anaylsis shows that treated purse seiners reduce their fishing
effort after PIPA implementation in the order of 16 hours per month.
This result is robust and significant (\emph{p \textless{} 0.05}) for
all model specifications, with the effect varying between
\(\beta_3 = -16.457\) and \(\beta_3 = -18.709\). Model specifications
that include the year polynomial show lower values for the \(\beta_1\)
coefficient associated to the \(Post_t\) policy dummy, and show positive
and negative values for \(\mu_1\) and \(\mu_2\), the linear and
cuadratic terms, respectively. These effectively represent the patterns
observed in Figure \{fig:all\_vessels\}.

Longliners show a similar pattern of effort reduction. However, the
magnitude of the \(\beta_3\) coefficient is smaller (ranging from
\(\beta_3 = -9.851\) to \(\beta_3 = -14.850\)) and not significant
across all model specifications. This, along with higher standard error
values suggest that longliners have a smaller and more variable response
to the implementation of LSMPAs.

Regressions coefficients for each gear type are shown in Tables
\ref{tab:purse} and \ref{tab:long}. Column (1) presents the DiD
regression with no fixed effects, column (2) includes month fixed
effects, column (3) includes month and the second degree polynomial for
years, and column (4) includes all of the above and country-level fixed
effects.

\begin{table}[!htbp] \centering 
  \caption{\label{tab:purse}Fishing hours from GFW for purse seiners (n = 106; 38 control, 68 treatment). Asterisks indicate significance levels. Numbers in parenthesis represent heteroskedastic-robust standard errors.} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lcccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{4}{c}{\textit{Dependent variable:}} \\ 
\cline{2-5} 
\\[-1.8ex] & \multicolumn{4}{c}{hours} \\ 
\\[-1.8ex] & (1) & (2) & (3) & (4)\\ 
\hline \\[-1.8ex] 
 post & 95.087$^{***}$ & 99.232$^{***}$ & 38.349$^{***}$ & 41.920$^{***}$ \\ 
  & (5.877) & (5.453) & (7.423) & (8.214) \\ 
  & & & & \\ 
 treated & $-$6.575 & $-$5.597 & $-$3.811 & 6.541 \\ 
  & (4.985) & (4.564) & (4.247) & (5.195) \\ 
  & & & & \\ 
 year &  &  & 12,828.900$^{***}$ & 16,665.590$^{***}$ \\ 
  &  &  & (2,451.444) & (3,717.658) \\ 
  & & & & \\ 
 year2 &  &  & $-$3.178$^{***}$ & $-$4.131$^{***}$ \\ 
  &  &  & (0.609) & (0.923) \\ 
  & & & & \\ 
 post:treated & $-$16.457$^{**}$ & $-$16.739$^{***}$ & $-$17.304$^{***}$ & $-$18.709$^{***}$ \\ 
  & (6.856) & (6.460) & (6.254) & (6.787) \\ 
  & & & & \\ 
 Constant & 59.490$^{***}$ & 65.485$^{***}$ & $-$12,946,334.000$^{***}$ & $-$16,807,078.000$^{***}$ \\ 
  & (4.422) & (6.132) & (2,473,372.000) & (3,759,572.000) \\ 
  & & & & \\ 
\hline \\[-1.8ex] 
Month FE & No & Yes & Yes & Yes \\ 
Flag FE & No & No & No & Yes \\ 
Observations & 3,867 & 3,867 & 3,867 & 3,481 \\ 
R$^{2}$ & 0.171 & 0.243 & 0.281 & 0.299 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{4}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table}

\begin{table}[!htbp] \centering 
  \caption{\label{tab:long}Fishing hours from GFW for longliners (n = 203; 88 control, 115 treatment). Asterisks indicate significance levels. Numbers in parenthesis represent heteroskedastic-robust standard errors.} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lcccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{4}{c}{\textit{Dependent variable:}} \\ 
\cline{2-5} 
\\[-1.8ex] & \multicolumn{4}{c}{hours} \\ 
\\[-1.8ex] & (1) & (2) & (3) & (4)\\ 
\hline \\[-1.8ex] 
 post & $-$11.929 & $-$6.968 & $-$15.550 & $-$6.761 \\ 
  & (7.969) & (7.975) & (10.181) & (11.289) \\ 
  & & & & \\ 
 treated & 70.142$^{***}$ & 72.314$^{***}$ & 71.985$^{***}$ & 14.026$^{*}$ \\ 
  & (7.200) & (7.200) & (7.279) & (7.988) \\ 
  & & & & \\ 
 year &  &  & $-$6,673.971$^{*}$ & 21,188.090$^{***}$ \\ 
  &  &  & (3,606.793) & (5,631.642) \\ 
  & & & & \\ 
 year2 &  &  & 1.657$^{*}$ & $-$5.259$^{***}$ \\ 
  &  &  & (0.894) & (1.398) \\ 
  & & & & \\ 
 post:treated & $-$9.851 & $-$12.290 & $-$12.779 & $-$14.850 \\ 
  & (9.294) & (9.262) & (9.334) & (9.563) \\ 
  & & & & \\ 
 Constant & 474.478$^{***}$ & 449.960$^{***}$ & 6,719,355.000$^{*}$ & $-$21,341,371.000$^{***}$ \\ 
  & (6.328) & (9.440) & (3,633,994.000) & (5,644,837.000) \\ 
  & & & & \\ 
\hline \\[-1.8ex] 
Month FE & No & Yes & Yes & Yes \\ 
Flag FE & No & No & No & Yes \\ 
Observations & 9,460 & 9,460 & 9,460 & 8,269 \\ 
R$^{2}$ & 0.027 & 0.041 & 0.042 & 0.094 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{4}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table}

Recall that to evaluate the redistribution of fishing effort we only
track fishing vessels that belong to the treated group. In this case, we
calculate the prportion of fishing effort allocated every month to each
spatially explicit region outlined by EEZs and the high seas. For purse
seiners, these represent 9 main EEZs, PIPA, the high seas, and a group
of other EEZs. Figure \ref{fig:redist_trend_ps} shows the monthly
relative fishing hours that each region received by all 183 treated
vessels. The top-left pannel shows the change in fishing effort inside
PIPA, including the preemtive fishing and immediate reduction previously
reported \citep{mcdermott_2018}.

The change in the relative allocation fishing effort by purse seiners
increases in eight of the 12 regions after PIPA implementation
\ref{tab:disp_mod}. The largest increase is observed for the I-Kiribati
EEZ, with an average increase of 0.11 (\emph{p \textless{} 0.001}). In
other words, the redistribution of treated vessels caused a 10\%
increase in the \emph{relative} allocation of fishing effort within
I-Kiribati waters. The only decrease is observed for Papua New Guinea,
but the coefficient is not significant. Figure \ref{fig:map_change_ps}
provides a spatial representation of these changes. It is evident that
the increase in relative fishing effort is greater for for regions
closer to PIPA.

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-15-1.pdf}
\caption{\label{fig:unnamed-chunk-15}\label{fig:redist_trend_ps}}
\end{figure}

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-18-1.pdf}
\caption{\label{fig:unnamed-chunk-18}\label{fig:map_change_ps}}
\end{figure}

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-19-1.pdf}
\caption{\label{fig:unnamed-chunk-19}\label{fig:map_change_ps}}
\end{figure}

\begin{table}[!htbp] \centering 
  \caption{\label{tab:disp_mod}Change in the relative allocation of fishing hours by purse seiners for each region. Asterisks indicate significance levels. Numbers in parenthesis represent heteroskedastic-robust standard errors.} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{1}{c}{\textit{Dependent variable:}} \\ 
\cline{2-2} 
\\[-1.8ex] & h\_prop \\ 
\hline \\[-1.8ex] 
 post & $-$0.085$^{***}$ (0.018) \\ 
  countryKIR & 0.251$^{***}$ (0.036) \\ 
  countryHS & $-$0.089$^{***}$ (0.018) \\ 
  countryCOK & $-$0.085$^{***}$ (0.018) \\ 
  countryFSM & $-$0.034 (0.021) \\ 
  countryMHL & $-$0.063$^{***}$ (0.019) \\ 
  countryNRU & $-$0.039$^{**}$ (0.020) \\ 
  countryPNG & 0.098$^{***}$ (0.034) \\ 
  countrySLB & $-$0.023 (0.026) \\ 
  countryTKL & $-$0.072$^{***}$ (0.018) \\ 
  countryTUV & $-$0.024 (0.021) \\ 
  countryothers & 0.016 (0.021) \\ 
  post:countryKIR & 0.113$^{**}$ (0.045) \\ 
  post:countryHS & 0.085$^{***}$ (0.018) \\ 
  post:countryCOK & 0.089$^{***}$ (0.018) \\ 
  post:countryFSM & 0.091$^{***}$ (0.025) \\ 
  post:countryMHL & 0.080$^{***}$ (0.021) \\ 
  post:countryNRU & 0.087$^{***}$ (0.021) \\ 
  post:countryPNG & $-$0.015 (0.037) \\ 
  post:countrySLB & 0.107$^{***}$ (0.031) \\ 
  post:countryTKL & 0.087$^{***}$ (0.019) \\ 
  post:countryTUV & 0.100$^{***}$ (0.025) \\ 
  post:countryothers & 0.201$^{***}$ (0.028) \\ 
  Constant & 0.089$^{***}$ (0.018) \\ 
 \hline \\[-1.8ex] 
Month FE & No \\ 
Observations & 864 \\ 
R$^{2}$ & 0.557 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{1}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table}

\section{Discusion}\label{discusion}

Our findings provide interesting insights into the effect that LSMPAs
can have on vessel behavior and the redistribution of fishing effort.
These collection of results shows that the implementation of PIPA caused
treated vessels to redeuce their fishing hours, and that this effect is
greater for purse seiners. Even though treated vessels fish less, their
relative allocation of fishing hours increased for all other fishing
grouds. This fidnings does not imply that there is more fishing effort,
but rather that each region receives a greater portion of the post-PIPA
fishing effort (which is lower than pre-PIPA). In this section we
discuss the implications of vessel-level reductions in fishing effort
and the increase in relative allocation of the remaining effort through
space. We also provide plausible explanations as to why purse seiners
seem to be more reactive to the spatial closure.
